%-------------------------------------------------------------------------------
%	PREAMBLE

\documentclass[10pt,letter,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

% packages
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\usepackage{textcomp}
\usepackage[numbers]{natbib}

% custom commands
\newcommand{\myphone}{(612) 817--7989}
\newcommand{\myemail}{ctastad@gmail.com}
\newcommand{\company}{***}
\newcommand{\role}{***}

% contact info
\name{Christopher}{Tastad}
%\address{720 Washington Ave S \#507}{Minneapolis, MN 55415}{USA}
\address{}{}{}
\phone[fixed]{\myphone{}}
\email{\myemail{}}
\social[github]{ctastad}
\social[linkedin]{ctastad}

\begin{document}

%-------------------------------------------------------------------------------
%   LETTER

\title{Letter}
\recipient{HR Department}{\company{} \\ STREET ADDRESS \\ CITY, STATE ZIP}
\date{\today}
\opening{To Whom It May Concern,}
\closing{Sincerely Yours,}
\enclosure[Attached]{Resume}
\makelettertitle{}

% General opener
I am interested in applying for the \role{} position with \company{}. With my background, I provide a unique blend of content knowledge, technical analysis, and relevant experience that make me a strong fit for the role. I have brought this aptitude together through a few core principles which I have applied in a diverse range of settings. Critical thinking and objectivity guide my approach; independence and competency carry to completion; and an attraction towards establishing effective systems elevates outcomes.

% Asakura lab
My first and most prominent experience was in stem cell development with a disease model of muscular dystrophy. As a research associate in The Stem Cell Institute, I worked in a central role through independent project coordination, grant and manuscript writing, lab member training, and overall lab management. While serving in this position, I employed strict research methodology and analysis to produce publication quality data. With that, I often presented and defended my efforts to both my primary investigator and the broader scientific community. The product of this work led to several co-authorships in high impact journals as well as being awarded individual grant monies with contributions to lab-wide grants.

% Informatics for analysis
Additionally, in recent history, I have focused in the study of handling large data sets, particularly in Bioinformatics. As an integrative field, I've brought my medical content knowledge forward with the development of advanced skill sets in statistical and computational modeling. By developing expertise in this area, I have drastically expanded the nature, flexibility, and application of the analytics capabilities that underline my scientific training. Most importantly, my ability to work with large data sets has become subject agnostic and can translate to any intensive technical task, all of which would be well suited to \company{}'s business objectives.

% General closer
Taken together, I would appreciate further consideration and an opportunity to interview with \company{} for the \role{} role. Please feel free to contact me at \myphone{} or \myemail{}.

\makeletterclosing{}
\clearpage

%-------------------------------------------------------------------------------
%   RESUME

\title{Resume}
\makecvtitle{}
\vspace{-1.0cm}

\section{Education}
\cventry{Sept 2015 --- Present}{University of Minnesota}{Bioinformatics, MS}{Minneapolis, MN}{Bioinformatics and Computational Biology}{}
\cventry{Sept 2007 --- May 2011}{University of Minnesota}{Biochemistry, BS}{Minneapolis, MN}{College of Biological Sciences}{}

%-------------------------------------------------------------------------------
%   SKILLS

\section{Skills}

\cvitem{Languages}{\textsc{R}, \textsc{bash}, \textrm{\LaTeX}, \textsc{sql}, \textsc{html}, \textsc{css}, \textsc{xml}}
\cvitem{Platforms}{Linux, \textsc{git}, \textsc{nginx}, \textsc{apache}, Relational Databases, Oracle, Vim, wordpress,
virtual machines, proxmox, docker containerization, HPC, vector graphics, visualization}
\cvitem{Packages}{rmarkdown, shiny, ggplot2, dplyr, tidyr, BioC, SummarizedExperiment, DNAcopy, GRL PACKAGES}
\cvitem{Genomics}{samtools, bwa-mem, CNV (VarScan2, Excavator), Single Cell (Seurat)}
\cvitem{Statistics}{Hypothesis testing, Simple/Multiple/Poisson Regression, A/B Testing, Contingency Testing, ANOVA, Survival Analysis, K-means, PCA, K-nearest neighbor, SVM,
Bayesian Networks, Functional Linkage Networks}
\cvitem{Benchwork}{DNA/RNA/protein isolation and analysis, western blotting, PCR, ELISA, luciferase, immunostaining, histology, epigenetic analysis, FACS, mammalian cell
culture}

%-------------------------------------------------------------------------------
%   EXPERIENCE

\section{Experience}
% starrlab research assistant
\cventry{May 2019 --- Present}{Department of OBGYN}{Graduate Research Assistant}{Minneapolis, MN}{Starr Lab}{%
    \begin{itemize}
        \item{test}
        \item{}
        \item{}
\end{itemize}}

% load planner
\cventry{Oct 2018 --- Present}{United Parcel Service}{Load Planner}{Minneapolis, MN}{Industrial Engineering}{%
    \begin{itemize}
        \item{Central point person in coordinating all hub-wide load related functions; mediating hub, feeder, and engineering priorities.}
        \item{Advance district level interests through industrial engineering functions of operational, flow, and system analysis.}
        \item{Operate with a wide latitude in exploring opportunities for cost saving measures for management and stakeholders.}
\end{itemize}}

% ups supervisor
\cventry{Oct 2017 --- Oct 2018}{United Parcel Service}{Supervisor}{Minneapolis, MN}{Small Sort}{%
    \begin{itemize}
        \item{Managed a team of 35 employees in largest operational unit in the Northern Plains District HQ sort hub.}
        \item{Brought an immediate 15\% production increase to area within first month with sustained production improvements.}
        \item{Developed and led significant improvement projects around personnel training, volume recovery, and missort reduction.}
\end{itemize}}

% ups hourly
\cventry{June 2017 --- Oct 2017}{United Parcel Service}{Package Sorter}{Minneapolis, MN}{}{}

% nmdp research assistant
\cventry{Jan 2016 --- July 2017}{National Marrow Donor Program}{Graduate Research Assistant}{Minneapolis, MN}{Bioinformatics}{%
    \begin{itemize}
        \item{Employed scientific method as an investigator in a big data R\&D department with a focus in hematological cancer treatment.}
        \item{Took both basic and clinical approach to investigation in cell therapy, immunology, and organ transplant genetics.}
        \item{Conducted analysis through R with Rstudio, Rmarkdown, and Rshiny, Python, and NextGen Sequencing data pipelines.}
\end{itemize}}

% biorepository tech
\cventry{Sept 2014 --- Jan 2016}{National Marrow Donor Program}{Biorepository Technician}{New Brighton, MN}{Research Repository}{%
    \begin{itemize}
        \item{Was responsible for research specimen processing in high-throughput clinical laboratory facility.}
        \item{Managed database and long-term storage for FDA and Bone Marrow Transplant Clinical Trials Network samples using GLP.}
        \item{Contributed to larger registry activities maintaining Be The Match patient/donor sample receiving, storage and typing.}
\end{itemize}}

% mpls club server
\cventry{Oct 2013 --- Sept 2014}{Minneapolis Club}{Banquet and Dining Server}{Minneapolis, MN}{}{%
    \begin{itemize}
        \item{Worked setup, service, and take down for dining room and banquets ranging from chef$'$s table dinners to events of 500+.}
        \item{Trained in the manner of French service and hospitality to maintain an elite level of accommodation and experience.}
        \item{Contributed to maintenance and building upkeep when necessary.}
\end{itemize}}

% face to face
\cventry{July 2012 --- Jan 2014}{Face to Face Organics LLC.}{Co-founder}{St.\ Anthony, MN}{}{%
    \begin{itemize}
        \item{Co-founded a personal care products start up that connected social activism with our product and its use.}
        \item{Deployed company$'$s operating software stack on limited budget with minimal upfront cost and sustained overhead.}
        \item{Contributed software proficiency in e-commerce, CRM, distribution, logistics, accounting, sales tracking, and inventory.}
\end{itemize}}

% asakura lab
\cventry{Dec 2007 --- Jan 2013}{The Stem Cell Institute}{Research Associate}{Minneapolis, MN}{Asakura Lab}{%
    \begin{itemize}
        \item{Conducted basic science research with a focus in skeletal muscle development, receiving 4 co-authorships.}
        \item{Well versed in full spectrum of molecular biology, histology and cell biology wet lab techniques and diagnostics.}
        \item{Contributed significant writing efforts toward group manuscripts and major grant awards, including a sucessful R01 bid.}
\end{itemize}}

% 2004 teaching assistant
\cventry{Sept 2009 --- May 2012}{University of Minnesota}{Teaching Assistant}{St.\ Paul, MN}{CBS Biol2004}{%
    \begin{itemize}
        \item{Led teaching lab that included an integrative, research-focused curriculum, highlighting significant independent discovery.}
        \item{Was consistently called on by course instructor for consultation in the improvement of course materials and curriculum.}
        \item{Received highest rating among all course TAs as indicated by students in post-semester evaluations for 2012 year.}
\end{itemize}}

% mslc
\cventry{Oct 2009 --- July 2012}{Minnesota Student Legislative Coalition}{Founder, Lobbyist, and Chairman}{Minneapolis, MN}{}{%
    \begin{itemize}
        \item{United leaders from all 5 U of MN campuses to form the active student lobby, earning the University$'$s endorsement.}
        \item{Directed issues involving education funding, loan rates, textbook pricing, campus safety, and veteran accreditation.}
        \item{Trained and supervised a team that guided the authorship of 4 student-specific bills during 2012 state legislative session.}
\end{itemize}}

%-------------------------------------------------------------------------------
%	PERSONAL

\section{Personal}
\cvitem{Hobbies}{Racquetball, CAD design \& 3d printing, Camping, Fishing, Hunting, Reading, Self-hosting software}
\subsection{Volunteering}
% trinity
\cventry{July 2017 --- Present}{Trinity Lutheran Church of Montevideo}{IT Consultant}{Montevideo, MN}{}{}
% recwell
\cventry{July 2017 --- July 2017}{University of Minnesota}{Youth Camp Racquetball Coach}{Minneapolis, MN}{Recwell}{}
% shriners
\cventry{Dec 2008 --- May 2013}{Shriners Hospital for Children}{Child Life Specialist}{Minneapolis, MN}{}{}
% ducks unlimited
\cventry{Nov 2008 --- July 2011}{Ducks Unlimited}{IT Consultant \& Umn Chapter Co-founder}{Edina, MN}{}{}
% south africa
\cventry{June 2009 --- July 2009}{Student Travel and Exposure South Africa}{Trauma Ward Aide}{Cape Town, South Africa}{}{}

%-------------------------------------------------------------------------------
%	PUBLICATIONS

\bibliographystyle{unsrt}
\nocite{refsearch,pmid22848585,pmid21425413,pmid20956382,pmid20705734}
\bibliography{publications}

%-------------------------------------------------------------------------------
%	AWARDS

\section{Awards}
\cvlanguage{Advocate of the Year}{University of Minnesota Alumni Association}{Oct, 2012}
\cvlanguage{Spirit of MSA (MVP)}{Minnesota Student Association}{May, 2012}
\cvlanguage{Highest Rated TA}{CBS Biol2004 Lab Students}{May, 2012}
\cvlanguage{Research Fellowship}{Gregory Marzolf Jr. Foundation}{Sept, 2009}
\cvlanguage{Distinct Honor --- Presenter's Award}{LHI/SCI Building Muscle and Blood Conference}{Oct, 2009}
\cvlanguage{Undergraduate Research Opportunity Grant}{University of Minnesota}{2008, 2009, 2011}

\end{document}
